Descriptive norms caused increases in mask wearing during the COVID-19 pandemic

### 2023-07-24 appendix.Rmd
update supp materials

\renewcommand{\appendixname}{\textbf{Supplementary Material}}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}
\pagenumbering{gobble}

#

@@

(ref:plotDAGCaption) _Directed acyclic graph reflecting causal assumptions._ In this model, a general unobserved sensitivity to social norms (NormSens) causes perceptions of descriptive social norms (DesNorm) and perceptions of injunctive social norms (InjNorm), and perceptions of descriptive and injunctive norms directly cause mask wearing (Mask). Perceptions of descriptive and injunctive norms also indirectly cause mask wearing through non-social beliefs, specifically factual beliefs (Fact) and personal normative beliefs (PersNorm). Finally, demographic variables such as gender, age, ethnicity, socioeconomic status, and political orientation (summarised as Demographics) are exogenous variables that are common causes of all other variables. Using the backdoor criterion[@Pearl1995], this causal model implies that it is necessary to control for perceptions of injunctive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived descriptive norms on mask wearing. Similarly, it is necessary to control for perceptions of descriptive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived injunctive norms on mask wearing.

@@

>>>>

\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}

# **Supplementary Material**

\setcounter{page}{1}
\small
\centering
\setlength\parindent{8mm}
Descriptive norms caused increases in mask wearing during the COVID-19 pandemic \newline
\hspace*{8mm} Samantha L. Heiman, Scott Claessens, Jessica D. Ayers, Diego Guevara Beltrán,\newline
\hspace*{8mm} Andrew Van Horn, Edward R. Hirt, Athena Aktipis & Peter M. Todd \newline
\normalsize
\raggedright
\setlength{\parindent}{40pt}
\newpage

@@

(ref:plotDAGCaption) _Directed acyclic graph reflecting causal assumptions._ In this model, a general unobserved sensitivity to social norms (NormSens) causes perceptions of descriptive social norms (DesNorm) and perceptions of injunctive social norms (InjNorm), and perceptions of descriptive and injunctive norms directly cause mask wearing (Mask). Perceptions of descriptive and injunctive norms also indirectly cause mask wearing through non-social beliefs, specifically factual beliefs (Fact) and personal normative beliefs (PersNorm). Finally, demographic variables such as gender, age, ethnicity, socioeconomic status, and political orientation (summarised as Demographics) are exogenous variables that are common causes of all other variables. Using the backdoor criterion (Pearl, 1995), this causal model implies that it is necessary to control for perceptions of injunctive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived descriptive norms on mask wearing. Similarly, it is necessary to control for perceptions of descriptive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived injunctive norms on mask wearing.

@@

\newpage
\setlength\parindent{0pt}

## Supplementary References

Pearl, J. (1995). Causal diagrams for empirical research. _Biometrika_, _82_(4), 669-688.

### 2023-07-24 manuscript.tex
update supp materials

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

\leavevmode\vadjust pre{\hypertarget{ref-Pearl1995}{}}%
\CSLLeftMargin{52. }%
\CSLRightInline{Pearl, J. \href{https://doi.org/10.2307/2337329}{Causal diagrams for empirical research}. \emph{Biometrika} \textbf{82}, 669--688 (1995).}

@@

\hypertarget{appendix-appendix}{%
\appendix}

\renewcommand{\appendixname}{\textbf{Supplementary Material}}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}
\pagenumbering{gobble}

\hypertarget{section}{%
\section{}\label{section}}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotDAG-1.pdf}
\caption{\label{fig:plotDAG}\emph{Directed acyclic graph reflecting causal assumptions.} In this model, a general unobserved sensitivity to social norms (NormSens) causes perceptions of descriptive social norms (DesNorm) and perceptions of injunctive social norms (InjNorm), and perceptions of descriptive and injunctive norms directly cause mask wearing (Mask). Perceptions of descriptive and injunctive norms also indirectly cause mask wearing through non-social beliefs, specifically factual beliefs (Fact) and personal normative beliefs (PersNorm). Finally, demographic variables such as gender, age, ethnicity, socioeconomic status, and political orientation (summarised as Demographics) are exogenous variables that are common causes of all other variables. Using the backdoor criterion\textsuperscript{52}, this causal model implies that it is necessary to control for perceptions of injunctive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived descriptive norms on mask wearing. Similarly, it is necessary to control for perceptions of descriptive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived injunctive norms on mask wearing.}
\end{figure}

@@

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

@@

\newpage
\vspace*{60mm}

\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}} \setcounter{equation}{0}

\hypertarget{supplementary-material}{%
\section{\texorpdfstring{\textbf{Supplementary Material}}{Supplementary Material}}\label{supplementary-material}}

\setcounter{page}{1}
\small
\centering
\setlength\parindent{8mm}

Descriptive norms caused increases in mask wearing during the COVID-19 pandemic \newline
\hspace*{8mm} Samantha L. Heiman, Scott Claessens, Jessica D. Ayers, Diego Guevara Beltrán,\newline
\hspace*{8mm} Andrew Van Horn, Edward R. Hirt, Athena Aktipis \& Peter M. Todd \newline
\normalsize

\raggedright
\setlength{\parindent}{40pt}
\newpage

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/plotDAG-1.pdf}
\caption{\label{fig:plotDAG}\emph{Directed acyclic graph reflecting causal assumptions.} In this model, a general unobserved sensitivity to social norms (NormSens) causes perceptions of descriptive social norms (DesNorm) and perceptions of injunctive social norms (InjNorm), and perceptions of descriptive and injunctive norms directly cause mask wearing (Mask). Perceptions of descriptive and injunctive norms also indirectly cause mask wearing through non-social beliefs, specifically factual beliefs (Fact) and personal normative beliefs (PersNorm). Finally, demographic variables such as gender, age, ethnicity, socioeconomic status, and political orientation (summarised as Demographics) are exogenous variables that are common causes of all other variables. Using the backdoor criterion (Pearl, 1995), this causal model implies that it is necessary to control for perceptions of injunctive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived descriptive norms on mask wearing. Similarly, it is necessary to control for perceptions of descriptive norms, factual beliefs, personal normative beliefs, and all demographics to estimate the direct causal effect of perceived injunctive norms on mask wearing.}
\end{figure}

@@

\newpage
\setlength\parindent{0pt}

\hypertarget{supplementary-references}{%
\subsection{Supplementary References}\label{supplementary-references}}

Pearl, J. (1995). Causal diagrams for empirical research. \emph{Biometrika}, \emph{82}(4), 669-688.
